Supplementary methods and results

### 2022-03-06 supplementary.Rmd
Compute SEM and its CI coefficients

>>>>

# SEM

```{r}
loadd(slope_com_var_no_covar, st_mono_trends_rich_bm)
library(piecewiseSEM)
library(semEff)
```

```{r}
  sem_tps = list(
    lm(
      ct_ff ~ log_bm_std + log_rich_std,
      data = filter(slope_com_var_no_covar, station %in% st_mono_trends_rich_bm),
      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
        ct_ff_strd_error
      ),
    lm(
      w_trph_lvl_avg ~ log_bm_std + log_rich_std,
      data = filter(slope_com_var_no_covar, station %in% st_mono_trends_rich_bm),
      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
        w_trph_lvl_avg_strd_error
      ),
    lm(
      log_bm_std ~ log_rich_std,
      data = filter(slope_com_var_no_covar, station %in% st_mono_trends_rich_bm),
      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error
    )
    )
sem <- list(
  lm(ct_ff ~ log_bm_std + log_rich_std, data = ti,
    weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
      ct_ff_strd_error),
    lm(w_trph_lvl_avg ~ log_bm_std + log_rich_std, data = ti,
      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
        w_trph_lvl_avg_strd_error),
      lm(log_bm_std ~ log_rich_std, data = ti,
        weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error
        )
)
plot(as.psem(sem))
```

```{r}
semeff_tps <- semEff(sem_tps, R = 1000, seed = 13, parallel = "no")
semeff <- semEff(sem, R = 1000, seed = 13, parallel = "no")
```

```{r}
loadd(sp_st_data)
library(nlme)

data_sp_sem <- na.omit(sp_st_data)
tuu <- get_mod_list(.data = data_sp_sem)

sp_sem <- list(
     log_rich_std = lmer(log_rich_std ~ log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
     log_bm_std = lmer(log_bm_std ~ log_rich_std + log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
     ct_ff = lmer(ct_ff ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
     w_trph_lvl_avg = lmer(w_trph_lvl_avg ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 +
       (1 | basin), data = data_sp_sem)
)
summary(sp_sem[[4]])
sp_psem <- as.psem(sp_sem)
summary_sp_sem <- summary(sp_psem)
plot(sp_psem, node_attrs = data.frame(shape = "rectangle", color = "black",
    fillcolor = "grey"))

sp_semeff <- semEff(sp_sem, R = 1000, seed = 13, parallel = "no", type = "parametric")
```

```{r}
sp_semeff_df <- from_semEff_to_table(x = sp_semeff)
semeff_df <- from_semEff_to_table(x = semeff)
```

```{r}
get_CI_sem_bootEFF <- function(booteff = NULL) {
  bootci <- bootCI(booteff)

  map_dfr(bootci, function(x) {
    # get rid of the table header  
    tab <- x[-1, ]
    # keep predictor name
    predictor <- tab[[1]]
    numeric_table <- map(tab, as.numeric)
    # suppr table columns
    mask_chr_column <- map_lgl(numeric_table, ~all(is.na(.x)))
    cbind(
      data.frame(predictor = predictor),
      tab[, !mask_chr_column]
    )
}, .id = "response")

}
get_CI_sem_bootEFF(test)
```

```{r}
```
